Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-26 paper/snakemajoranas.tex
add ref

\comment{SNS junctions also work and require smaller field.}
Recently, a modified setup has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductor-normal-superconductor (SNS) junction.
The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.

>>>>

\comment{SNS junctions also work and require smaller field.}
Recently, a modified setup has been proposed\cite{pientka2017topological,hell2017two} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
Two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
